2016 Brussels Bombings

### 2019-05-27 report/report.Rmd
Fix: air space -> airspace

Finally, the animation below showcases the flights over Belgium and its surrounding countries over the course of the day of the tragic events. It can be seen that there is no significant change regarding the country's air space:

@@

Note that there is a notable peak during the 20th of March, when an air traffic control strike over France paralyzed the french air space and caused numerous delays. Any flight that was scheduled to fly over France suffered from delays. In any case, that peak in the delays is not related to the incident being analyzed.

>>>>

Finally, the animation below showcases the flights over Belgium and its surrounding countries over the course of the day of the tragic events. It can be seen that there is no significant change regarding the country's airspace:

@@

Note that there is a notable peak during the 20th of March, when an air traffic control strike over France paralyzed the french airspace and caused numerous delays. Any flight that was scheduled to fly over France suffered from delays. In any case, that peak in the delays is not related to the incident being analyzed.
